Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2024-02-15 src/tex/ms.tex
[showyourwork] overleaf sync

% Filler text
\usepackage{blindtext}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{showyourwork}
\usepackage[autostyle]{csquotes}
\usepackage{amssymb}
\let\tablenum\relaxgit 
\usepackage{siunitx}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator{\arcsinh}{arcsinh}
\newcommand{\chandra}{\textit{Chandra}~}
\newcommand{\chandranospace}{\textit{Chandra}}
\newcommand{\xmm}{\textit{XMM}~}
\newcommand{\fermi}{\textit{Fermi}-LAT~}
\newcommand{\ferminospace}{\textit{Fermi}-LAT}
\newcommand{\jolideco}{\textit{Jolideco}~}
\newcommand{\jolideconospace}{\textit{Jolideco}}
\newcommand{\aposteriori}{a~posteriori~}
\newcommand{\aprioir}{a~priori~}
\newcommand{\gammaray}{$\gamma$-ray\xspace}
\newcommand{\xray}{X-ray\xspace}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

@@

    ]
    \begin{table}
    \centering
        \begin{tabular}{ c|c|c|c|c|c } 
            \input{output/metrics-table.tex}
        \end{tabular}
        \label{tab:metrics}
        \script{metrics-table.py}
        \caption{Image metrics for the difference source scenarios and methods.}
    \end{table}

>>>>

% Filler text
\usepackage{blindtext}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{showyourwork}
\usepackage[autostyle]{csquotes}
\usepackage{amssymb}
\usepackage{makecell}
\let\tablenum\relaxgit 
\usepackage{siunitx}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator{\arcsinh}{arcsinh}

%\renewcommand\theadalign{bc}

\newcommand{\chandra}{\textit{Chandra}~}
\newcommand{\chandranospace}{\textit{Chandra}}
\newcommand{\xmm}{\textit{XMM}~}
\newcommand{\fermi}{\textit{Fermi}-LAT~}
\newcommand{\ferminospace}{\textit{Fermi}-LAT}
\newcommand{\jolideco}{\textit{Jolideco}~}
\newcommand{\jolideconospace}{\textit{Jolideco}}
\newcommand{\aposteriori}{a~posteriori~}
\newcommand{\aprioir}{a~priori~}
\newcommand{\gammaray}{$\gamma$-ray\xspace}
\newcommand{\xray}{X-ray\xspace}
\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

@@

    ]
    \begin{table*}
    \centering
        \begin{tabular}{ c|c|c|c|c|c } 
            \input{output/metrics-table.tex}
        \end{tabular}
        \label{tab:metrics}
        \script{metrics-table.py}
        \caption{Image metrics for the difference source scenarios and methods shown in Figure~\ref{fig:comparison-scenarios}. The first number in a cell shows the structural similarity index (the closer to one the better ) and the second number shows the normalized root mean square (the lower the better).}
    \end{table*}
